Submission and Formatting Instructions for \\ International Conference on Machine Learning (ICML 2016)

### 2016-02-03 icml2016/paper.tex
Added to paper.

\subsection{Scalable and Amortized Inference}
\label{subsec:scale}

@@

>>>>

\subsection{Scalable and Amortised Inference}
\label{subsec:scale}

@@

Amortised inference ... VAE, back-constraints, ... we test several options: MLP vs kernel, q(X) vs r(U,X)...

\section{TO DO:}
\begin{itemize}
  \item Graphs for the 3 models.
\end{itemize}

\section{NOTES}

From another perspective, the partial feedback of of z to the aux params (captured in r) means that there is a term in the cost function (aux lower bound) which is a direct effect of the generative power of aux params to generate z - an indirect is achieved when z is first passed through the generative model. So direct feedback is a reinforce step - it reinforces our current belief over z. It endows the scheme with a memory!

The above is for the aux lower lower bound in general, but we have even more motivation to use it in the case of the GP-LVM-CMF: want to avoid having to do optimization to make a prediction of a new data point!
